PRICE, HOST, AMENITIES, LOCATION

```{r}
#Library 
library(dplyr)
library(tidytext)
library(tidyr)
library(tm)
library(plotly)
library(wordcloud)
library(wordcloud2)
library(SnowballC)
library(stringr)
library(reshape2)
library(ggplot2) 
library(NLP) 
library(RColorBrewer) 
library(syuzhet)
```

READ DATASET 
```{r}
#read data
setwd("D:/Users/Acer User/Documents")
price <- read.csv("price.csv")
host <- read.csv("host.csv")
amenities <- read.csv("amenities.csv")
location<- read.csv("location.csv")
```

```{r}
#REMOVE DUPLICATION
#remove duplication
distinct(price,.keep_all=TRUE)
distinct(host,.keep_all=TRUE)
distinct(amenities,.keep_all=TRUE)
distinct(location,.keep_all=TRUE)

#To check the number of missing values
sapply(price, function(x) sum(is.na(x)))
sapply(host, function(x) sum(is.na(x)))
sapply(amenities, function(x) sum(is.na(x)))
sapply(location, function(x) sum(is.na(x)))

```
SPLIT PRICE INTO ASIAN WESTERN
```{r}
price_asian <- subset(price,price$resident=='asian')
price_west <- subset(price,price$resident=='western')
```


PRICE SENTIMENT
```{r}
sentiment_price <-tidytext::unnest_tokens(read.csv("D:/Users/Acer User/Documents/price.csv"), word, Text)

sentiment_price %>%
  inner_join(get_sentiments("bing")) %>% # pull out only sentiment words
  count(sentiment) %>% # count of positive & negative words
  spread(sentiment, n, fill = 0) %>% # made data wide rather than narrow
  mutate(sentiment = positive - negative) # positive words -  negative words
# find out most common negative and positive words
bing_word_counts <- sentiment_price %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()
# show the word counts
bing_word_counts
# visualize the words by using ggplot
bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(5) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label=n), vjust=-0.2, size=3.0) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip()
sentiment_price %>%
  filter(word != "unknown") %>% 
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("purple", "maroon"),
                   max.words = 100)


```

PRICE ASIAN EMOTION CLASSIFICATION
```{r}
#sentiment analysis
syuzet_price_asian<- get_sentiment(price_asian$Text, method="syuzhet")
head(syuzet_price_asian)
#bing
bing_price_asian<- get_sentiment(price_asian$Text,method="bing")
head(bing_price_asian)
#afinn
afinn_price_asian<- get_sentiment(price_asian$Text,method="afinn")
#compare first row of each vector using sign function
rbind(
  sign(head(syuzet_price_asian)),
  sign(head(bing_price_asian)),
  sign(head(afinn_price_asian))
)
#Emotion classification
emotion_price_asian<- get_nrc_sentiment(price_asian$Text)
head(emotion_price_asian,10)


td_price_asian<-data.frame(t(emotion_price_asian))
td_price_asian_new <- data.frame(rowSums(td_price_asian[1:256]))
names(td_price_asian_new)[1] <- "count"
td_price_asian_new <-cbind("sentiment"=rownames(td_price_asian_new),td_price_asian_new)
rownames(td_price_asian_new) <- NULL
td_price_asian_new2 <-td_price_asian_new[1:8,]
quickplot(sentiment, data=td_price_asian_new2, 
          weight=count, geom="bar",fill="sentiment",
          ylab="count")+ggtitle("sentiments")
```


PRICE_ASIAN EMOTION SCORE
```{r}
anger <- sum(emotion_price_asian$anger)
anticipation <- sum(emotion_price_asian$anticipation)
disgust <- sum(emotion_price_asian$disgust)
fear <- sum(emotion_price_asian$fear)
joy <- sum(emotion_price_asian$joy)
sadness <- sum(emotion_price_asian$sadness)
surprise <- sum(emotion_price_asian$surprise)
trust <- sum(emotion_price_asian$trust)
total <- sum(anger,anticipation,disgust,fear,joy,sadness,surprise,trust)

price_asian_anger <- anger/total
price_asian_anticipation <- anticipation/total
price_asian_disgust <- disgust/total
price_asian_fear <- fear/total
price_asian_joy <- joy/total
price_asian_sadness <- sadness/total
price_asian_surprise <- surprise/total
price_asian_trust <- trust/total
rbind(price_asian_anger,price_asian_anticipation,price_asian_disgust,
      price_asian_fear,price_asian_joy,price_asian_sadness,
      price_asian_surprise,price_asian_trust)

sent_total <- sum(emotion_price_asian$negative,emotion_price_asian$positive)
pos <- sum(emotion_price_asian$positive)
neg <- sum(emotion_price_asian$negative)
price_asian_pos <- pos/sent_total
price_asian_neg <- neg/sent_total
rbind(price_asian_pos,price_asian_neg)
```
PRICE WESTERN EMOTION CLASSIFICATION
```{r}
#sentiment analysis
syuzet_price_west<- get_sentiment(price_west$Text, method="syuzhet")
head(syuzet_price_west)
#bing
bing_price_west<- get_sentiment(price_west$Text,method="bing")
head(bing_price_west)
#afinn
afinn_price_west<- get_sentiment(price_west$Text,method="afinn")
#compare first row of each vector using sign function
rbind(
  sign(head(syuzet_price_west)),
  sign(head(bing_price_west)),
  sign(head(afinn_price_west))
)
#Emotion classification
emotion_price_west<- get_nrc_sentiment(price_west$Text)
head(emotion_price_west,10)


td_price_west<-data.frame(t(emotion_price_west))
td_price_west_new <- data.frame(rowSums(td_price_west[1:60]))
names(td_price_west_new)[1] <- "count"
td_price_west_new <-cbind("sentiment"=rownames(td_price_west_new),td_price_west_new)
rownames(td_price_west_new) <- NULL
td_price_west_new2 <-td_price_west_new[1:8,]
quickplot(sentiment, data=td_price_west_new2, 
          weight=count, geom="bar",fill="sentiment",
          ylab="count")+ggtitle("sentiments")
```


PRICE_WESTERN EMOTION SCORE
```{r}
anger <- sum(emotion_price_west$anger)
anticipation <- sum(emotion_price_west$anticipation)
disgust <- sum(emotion_price_west$disgust)
fear <- sum(emotion_price_west$fear)
joy <- sum(emotion_price_west$joy)
sadness <- sum(emotion_price_west$sadness)
surprise <- sum(emotion_price_west$surprise)
trust <- sum(emotion_price_west$trust)
total <- sum(anger,anticipation,disgust,fear,joy,sadness,surprise,trust)

price_west_anger <- anger/total
price_west_anticipation <- anticipation/total
price_west_disgust <- disgust/total
price_west_fear <- fear/total
price_west_joy <- joy/total
price_west_sadness <- sadness/total
price_west_surprise <- surprise/total
price_west_trust <- trust/total
rbind(price_west_anger,price_west_anticipation,price_west_disgust,
      price_west_fear,price_west_joy,price_west_sadness,
      price_west_surprise,price_west_trust)

sent_total <- sum(emotion_price_west$negative,emotion_price_west$positive)
pos <- sum(emotion_price_west$positive)
neg <- sum(emotion_price_west$negative)
price_west_pos <- pos/sent_total
price_west_neg <- neg/sent_total
rbind(price_west_pos,price_west_neg)
```



HOST SENTIMENT
```{r}
sentiment_host <-tidytext::unnest_tokens(read.csv("D:/Users/Acer User/Documents/host.csv"), word, Text)

sentiment_host %>%
  inner_join(get_sentiments("bing")) %>% # pull out only sentiment words
  count(sentiment) %>% # count of positive & negative words
  spread(sentiment, n, fill = 0) %>% # made data wide rather than narrow
  mutate(sentiment = positive - negative) # positive words -  negative words
# find out most common negative and positive words
bing_word_counts <- sentiment_host  %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()
# show the word counts
bing_word_counts
# visualize the words by using ggplot
bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(5) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label=n), vjust=-0.2, size=3.0) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip()
sentiment_host %>%
  filter(word != "unknown") %>% 
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("purple", "maroon"),
                   max.words = 100)
```

SPLIT HOST INTO ASIAN WESTERN
```{r}
host_asian <- subset(host, host$resident=='asian')
host_west <- subset(host, host$resident=='western')
```


HOST ASIAN EMOTION
```{r}
#sentiment analysis
syuzet_host_asian<- get_sentiment(host_asian$Text, method="syuzhet")
head(syuzet_host_asian)
#bing
bing_host_asian <- get_sentiment(host_asian$Text,method="bing")
head(bing_host_asian)
#afinn
afinn_host_asian <- get_sentiment(host_asian$Text,method="afinn")
#compare first row of each vector using sign function
rbind(
  sign(head(syuzet_host_asian)),
  sign(head(bing_host_asian)),
  sign(head(afinn_host_asian))
)
#Emotion classification
emotion_host_asian <- get_nrc_sentiment(host_asian$Text)
head(emotion_host_asian,10)

td_host_asian <-data.frame(t(emotion_host_asian))
td_host_asian_new <- data.frame(rowSums(td_host_asian[1:97]))
names(td_host_asian_new)[1] <- "count"
td_host_asian_new <-cbind("sentiment"=rownames(td_host_asian_new),td_host_asian_new)
rownames(td_host_asian_new) <- NULL
td_host_asian_new2 <-td_host_asian_new[1:6,]
td_host_asian_new2 <-td_host_asian_new[1:8,]
quickplot(sentiment, data=td_host_asian_new2, 
          weight=count, geom="bar",fill="sentiment",
          ylab="count")+ggtitle("sentiments")


```
HOST_ASIAN EMOTION SCORE

```{r}
anger <- sum(emotion_host_asian$anger)
anticipation <- sum(emotion_host_asian$anticipation)
disgust <- sum(emotion_host_asian$disgust)
fear <- sum(emotion_host_asian$fear)
joy <- sum(emotion_host_asian$joy)
sadness <- sum(emotion_host_asian$sadness)
surprise <- sum(emotion_host_asian$surprise)
trust <- sum(emotion_host_asian$trust)
total <- sum(anger,anticipation,disgust,fear,joy,sadness,surprise,trust)

host_asian_anger <- anger/total
host_asian_anticipation <- anticipation/total
host_asian_disgust <- disgust/total
host_asian_fear <- fear/total
host_asian_joy <- joy/total
host_asian_sadness <- sadness/total
host_asian_surprise <- surprise/total
host_asian_trust <- trust/total
rbind(host_asian_anger,host_asian_anticipation,host_asian_disgust,
      host_asian_fear,host_asian_joy,host_asian_sadness,
      host_asian_surprise,host_asian_trust)

sent_total <- sum(emotion_host_asian$negative,emotion_host_asian$positive)
pos <- sum(emotion_host_asian$positive)
neg <- sum(emotion_host_asian$negative)
host_asian_pos <- pos/sent_total
host_asian_neg <- neg/sent_total
rbind(host_asian_pos,host_asian_neg)
```


HOST WESTERN EMOTION
```{r}
#sentiment analysis
syuzet_host_west<- get_sentiment(host_west$Text, method="syuzhet")
head(syuzet_host_west)
#bing
bing_host_west <- get_sentiment(host_west$Text,method="bing")
head(bing_host_west)
#afinn
afinn_host_west <- get_sentiment(host_west$Text,method="afinn")
#compare first row of each vector using sign function
rbind(
  sign(head(syuzet_host_west)),
  sign(head(bing_host_west)),
  sign(head(afinn_host_west))
)
#Emotion classification
emotion_host_west <- get_nrc_sentiment(host_west$Text)
head(emotion_host_west,10)

td_host_west <-data.frame(t(emotion_host_west))
td_host_west_new <- data.frame(rowSums(td_host_west[1:425]))
names(td_host_west_new)[1] <- "count"
td_host_west_new <-cbind("sentiment"=rownames(td_host_west_new),td_host_west_new)
rownames(td_host_west_new) <- NULL
td_host_west_new2 <-td_host_west_new[1:6,]
td_host_west_new2 <-td_host_west_new[1:8,]
quickplot(sentiment, data=td_host_west_new2, 
          weight=count, geom="bar",fill="sentiment",
          ylab="count")+ggtitle("sentiments")


```

HOST_WESTERN EMOTION SCORE

```{r}
anger <- sum(emotion_host_west$anger)
anticipation <- sum(emotion_host_west$anticipation)
disgust <- sum(emotion_host_west$disgust)
fear <- sum(emotion_host_west$fear)
joy <- sum(emotion_host_west$joy)
sadness <- sum(emotion_host_west$sadness)
surprise <- sum(emotion_host_west$surprise)
trust <- sum(emotion_host_west$trust)
total <- sum(anger,anticipation,disgust,fear,joy,sadness,surprise,trust)

host_west_anger <- anger/total
host_west_anticipation <- anticipation/total
host_west_disgust <- disgust/total
host_west_fear <- fear/total
host_west_joy <- joy/total
host_west_sadness <- sadness/total
host_west_surprise <- surprise/total
host_west_trust <- trust/total
rbind(host_west_anger,host_west_anticipation,host_west_disgust,
      host_west_fear,host_west_joy,host_west_sadness,
      host_west_surprise,host_west_trust)

sent_total <- sum(emotion_host_west$negative,emotion_host_west$positive)
pos <- sum(emotion_host_west$positive)
neg <- sum(emotion_host_west$negative)
host_west_pos <- pos/sent_total
host_west_neg <- neg/sent_total
rbind(host_west_pos,host_west_neg)
```

AMENITIES SENTIMENT ANALYSIS
```{r}
sentiment_amenities <-tidytext::unnest_tokens(read.csv("D:/Users/Acer User/Documents/amenities.csv"), word, Text)

sentiment_amenities %>%
  inner_join(get_sentiments("bing")) %>% # pull out only sentiment words
  count(sentiment) %>% # count of positive & negative words
  spread(sentiment, n, fill = 0) %>% # made data wide rather than narrow
  mutate(sentiment = positive - negative) # positive words -  negative words
# find out most common negative and positive words
bing_word_counts <- sentiment_amenities %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()
# show the word counts
bing_word_counts
# visualize the words by using ggplot
bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(5) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label=n), vjust=-0.2, size=3.0) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip()
sentiment_amenities %>%
  filter(word != "unknown") %>% 
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("purple", "maroon"),
                   max.words = 100)
```

SPLIT AMENITIES INTO ASIAN WESTERN
```{r}
amenities_asian <- subset(amenities,amenities$resident=='asian')
amenities_west <- subset(amenities,amenities$resident=='western')
```


AMENITIES ASIAN EMOTION
```{r}
#sentiment analysis
syuzet_amenities_asian <- get_sentiment(amenities_asian$Text, method="syuzhet")
head(syuzet_amenities_asian)
#bing
bing_amenities_asian<- get_sentiment(amenities_asian$Text,method="bing")
head(bing_amenities_asian)
#afinn
afinn_amenities_asian <- get_sentiment(amenities_asian$Text,method="afinn")
#compare first row of each vector using sign function
rbind(
  sign(head(syuzet_amenities_asian)),
  sign(head(bing_amenities_asian)),
  sign(head(afinn_amenities_asian))
)
#Emotion classification
emotion_amenities_asian <- get_nrc_sentiment(amenities_asian$Text)
head(emotion_amenities_asian,10)

td_amenities_asian <-data.frame(t(emotion_amenities_asian))
td_amenities_asian_new <- data.frame(rowSums(td_amenities_asian[1:240]))
names(td_amenities_asian_new)[1] <- "count"
td_amenities_asian_new <-cbind("sentiment"=rownames(td_amenities_asian_new),td_amenities_asian_new)
rownames(td_amenities_asian_new) <- NULL
td_amenities_asian_new2 <-td_amenities_asian_new[1:6,]
td_amenities_asian_new2 <-td_amenities_asian_new[1:8,]
quickplot(sentiment, data=td_amenities_asian_new2, 
          weight=count, geom="bar",fill="sentiment",
          ylab="count")+ggtitle("sentiments")
```

AMENITIES_ASIAN EMOTION SCORE
```{r}
anger <- sum(emotion_amenities_asian$anger)
anticipation <- sum(emotion_amenities_asian$anticipation)
disgust <- sum(emotion_amenities_asian$disgust)
fear <- sum(emotion_amenities_asian$fear)
joy <- sum(emotion_amenities_asian$joy)
sadness <- sum(emotion_amenities_asian$sadness)
surprise <- sum(emotion_amenities_asian$surprise)
trust <- sum(emotion_amenities_asian$trust)
total <- sum(anger,anticipation,disgust,fear,joy,sadness,surprise,trust)

amenities_asian_anger <- anger/total
amenities_asian_anticipation <- anticipation/total
amenities_asian_disgust <- disgust/total
amenities_asian_fear <- fear/total
amenities_asian_joy <- joy/total
amenities_asian_sadness <- sadness/total
amenities_asian_surprise <- surprise/total
amenities_asian_trust <- trust/total
rbind(amenities_asian_anger,amenities_asian_anticipation,amenities_asian_disgust,
      amenities_asian_fear,amenities_asian_joy,amenities_asian_sadness,
      amenities_asian_surprise,amenities_asian_trust)

sent_total <- sum(emotion_amenities_asian$negative,emotion_amenities_asian$positive)
pos <- sum(emotion_amenities_asian$positive)
neg <- sum(emotion_amenities_asian$negative)
amenities_asian_pos <- pos/sent_total
amenities_asian_neg <- neg/sent_total
rbind(amenities_asian_pos,amenities_asian_neg)
```

AMENITIES WESTERN EMOTION
```{r}
#sentiment analysis
syuzet_amenities_west <- get_sentiment(amenities_west$Text, method="syuzhet")
head(syuzet_amenities_west)
#bing
bing_amenities_west<- get_sentiment(amenities_west$Text,method="bing")
head(bing_amenities_west)
#afinn
afinn_amenities_west <- get_sentiment(amenities_west$Text,method="afinn")
#compare first row of each vector using sign function
rbind(
  sign(head(syuzet_amenities_west)),
  sign(head(bing_amenities_west)),
  sign(head(afinn_amenities_west))
)
#Emotion classification
emotion_amenities_west <- get_nrc_sentiment(amenities_west$Text)
head(emotion_amenities_west,10)

td_amenities_west <-data.frame(t(emotion_amenities_west))
td_amenities_west_new <- data.frame(rowSums(td_amenities_west[1:16]))
names(td_amenities_west_new)[1] <- "count"
td_amenities_west_new <-cbind("sentiment"=rownames(td_amenities_west_new),td_amenities_west_new)
rownames(td_amenities_west_new) <- NULL
td_amenities_west_new2 <-td_amenities_west_new[1:6,]
td_amenities_west_new2 <-td_amenities_west_new[1:8,]
quickplot(sentiment, data=td_amenities_west_new2, 
          weight=count, geom="bar",fill="sentiment",
          ylab="count")+ggtitle("sentiments")
```

AMENITIES_WESTERN EMOTION SCORE
```{r}
anger <- sum(emotion_amenities_west$anger)
anticipation <- sum(emotion_amenities_west$anticipation)
disgust <- sum(emotion_amenities_west$disgust)
fear <- sum(emotion_amenities_west$fear)
joy <- sum(emotion_amenities_west$joy)
sadness <- sum(emotion_amenities_west$sadness)
surprise <- sum(emotion_amenities_west$surprise)
trust <- sum(emotion_amenities_west$trust)
total <- sum(anger,anticipation,disgust,fear,joy,sadness,surprise,trust)

amenities_west_anger <- anger/total
amenities_west_anticipation <- anticipation/total
amenities_west_disgust <- disgust/total
amenities_west_fear <- fear/total
amenities_west_joy <- joy/total
amenities_west_sadness <- sadness/total
amenities_west_surprise <- surprise/total
amenities_west_trust <- trust/total
rbind(amenities_west_anger,amenities_west_anticipation,amenities_west_disgust,
      amenities_west_fear,amenities_west_joy,amenities_west_sadness,
      amenities_west_surprise,amenities_west_trust)

sent_total <- sum(emotion_amenities_west$negative,emotion_amenities_west$positive)
pos <- sum(emotion_amenities_west$positive)
neg <- sum(emotion_amenities_west$negative)
amenities_west_pos <- pos/sent_total
amenities_west_neg <- neg/sent_total
rbind(amenities_west_pos,amenities_west_neg)
```

LOCATION SENTIMENT ANALYSIS
```{r}
sentiment_location <-tidytext::unnest_tokens(read.csv("D:/Users/Acer User/Documents/location.csv"), word, Text)

sentiment_location %>%
  inner_join(get_sentiments("bing")) %>% # pull out only sentiment words
  count(sentiment) %>% # count of positive & negative words
  spread(sentiment, n, fill = 0) %>% # made data wide rather than narrow
  mutate(sentiment = positive - negative) # positive words -  negative words
# find out most common negative and positive words
bing_word_counts <- sentiment_location %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()
# show the word counts
bing_word_counts
# visualize the words by using ggplot
bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(5) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label=n), vjust=-0.2, size=3.0) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip()
sentiment_location %>%
  filter(word != "unknown") %>% 
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("purple", "maroon"),
                   max.words = 100)
```
SPLIT LOCATION INTO ASIAN WESTERN
```{r}
location_asian <- subset(location, location$resident=='asian')
location_west <- subset(location, location$resident=='western')
```



LOCATION ASIAN EMOTION
```{r}
#sentiment analysis
syuzet_location_asian <- get_sentiment(location_asian$Text, method="syuzhet")
head(syuzet_location_asian)
#bing
bing_location_asian<- get_sentiment(location_asian$Text,method="bing")
head(bing_location_asian)
#afinn
afinn_location_asian<- get_sentiment(location_asian$Text,method="afinn")
#compare first row of each vector using sign function
rbind(
  sign(head(syuzet_location_asian)),
  sign(head(bing_location_asian)),
  sign(head(afinn_location_asian))
)
#Emotion classification
emotion_location_asian <- get_nrc_sentiment(location_asian$Text)
head(emotion_location_asian,10)

td_location_asian <-data.frame(t(emotion_location_asian))
td_location_asian_new <- data.frame(rowSums(td_location_asian[1:166]))
names(td_location_asian_new)[1] <- "count"
td_location_asian_new <-cbind("sentiment"=rownames(td_location_asian_new),td_location_asian_new)
rownames(td_location_asian_new) <- NULL
td_location_asian_new2 <-td_location_asian_new[1:6,]
td_location_asian_new2 <-td_location_asian_new[1:8,]
quickplot(sentiment, data=td_location_asian_new2, 
          weight=count, geom="bar",fill="sentiment",
          ylab="count")+ggtitle("sentiments")
```


LOCATION_ASIAN EMOTION SCORE
```{r}
anger <- sum(emotion_location_asian$anger)
anticipation <- sum(emotion_location_asian$anticipation)
disgust <- sum(emotion_location_asian$disgust)
fear <- sum(emotion_location_asian$fear)
joy <- sum(emotion_location_asian$joy)
sadness <- sum(emotion_location_asian$sadness)
surprise <- sum(emotion_location_asian$surprise)
trust <- sum(emotion_location_asian$trust)
total <- sum(anger,anticipation,disgust,fear,joy,sadness,surprise,trust)

location_asian_anger <- anger/total
location_asian_anticipation <- anticipation/total
location_asian_disgust <- disgust/total
location_asian_fear <- fear/total
location_asian_joy <- joy/total
location_asian_sadness <- sadness/total
location_asian_surprise <- surprise/total
location_asian_trust <- trust/total
rbind(location_asian_anger,location_asian_anticipation,location_asian_disgust,
      location_asian_fear,location_asian_joy,location_asian_sadness,
      location_asian_surprise,location_asian_trust)
sent_total <- sum(emotion_location_asian$negative,emotion_location_asian$positive)
pos <- sum(emotion_location_asian$positive)
neg <- sum(emotion_location_asian$negative)
location_asian_pos <- pos/sent_total
location_asian_neg <- neg/sent_total
rbind(location_asian_pos,location_asian_neg)
```

LOCATION WESTERN EMOTION
```{r}
#sentiment analysis
syuzet_location_west<- get_sentiment(location_west$Text, method="syuzhet")
head(syuzet_location_west)
#bing
bing_location_west<- get_sentiment(location_west$Text,method="bing")
head(bing_location_west)
#afinn
afinn_location_west<- get_sentiment(location_west$Text,method="afinn")
#compare first row of each vector using sign function
rbind(
  sign(head(syuzet_location_west)),
  sign(head(bing_location_west)),
  sign(head(afinn_location_west))
)
#Emotion classification
emotion_location_west <- get_nrc_sentiment(location_west$Text)
head(emotion_location_west,10)

td_location_west <-data.frame(t(emotion_location_west))
td_location_west_new <- data.frame(rowSums(td_location_west[1:183]))
names(td_location_west_new)[1] <- "count"
td_location_west_new <-cbind("sentiment"=rownames(td_location_west_new),td_location_west_new)
rownames(td_location_west_new) <- NULL
td_location_west_new2 <-td_location_west_new[1:6,]
td_location_west_new2 <-td_location_west_new[1:8,]
quickplot(sentiment, data=td_location_west_new2, 
          weight=count, geom="bar",fill="sentiment",
          ylab="count")+ggtitle("sentiments")
```


LOCATION_WESTERN EMOTION SCORE
```{r}
anger <- sum(emotion_location_west$anger)
anticipation <- sum(emotion_location_west$anticipation)
disgust <- sum(emotion_location_west$disgust)
fear <- sum(emotion_location_west$fear)
joy <- sum(emotion_location_west$joy)
sadness <- sum(emotion_location_west$sadness)
surprise <- sum(emotion_location_west$surprise)
trust <- sum(emotion_location_west$trust)
total <- sum(anger,anticipation,disgust,fear,joy,sadness,surprise,trust)

location_west_anger <- anger/total
location_west_anticipation <- anticipation/total
location_west_disgust <- disgust/total
location_west_fear <- fear/total
location_west_joy <- joy/total
location_west_sadness <- sadness/total
location_west_surprise <- surprise/total
location_west_trust <- trust/total
rbind(location_west_anger,location_west_anticipation,location_west_disgust,
      location_west_fear,location_west_joy,location_west_sadness,
      location_west_surprise,location_west_trust)
sent_total <- sum(emotion_location_west$negative,emotion_location_west$positive)
pos <- sum(emotion_location_west$positive)
neg <- sum(emotion_location_west$negative)
location_west_pos <- pos/sent_total
location_west_neg <- neg/sent_total
rbind(location_west_pos,location_west_neg)
```